\documentclass[letterpaper,8pt]{article}
\usepackage{fancyhdr}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyperref}
\RequirePackage{fontawesome}

\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



\begin
    {center}\textbf{\huge \scshape Ananya Kakani} \\ \vspace{0.8pt} 
     % Boston,MA \\ \vspace{1pt}
    \small Boston, MA$|$ +1(857)313-4454 $|$ \href{mailto:kakani.a@northeastern.edu} {\textcolor{blue}{\underline{kakani.a@northeastern.edu}}} $|$ 
    \href{https://www.linkedin.com/in/AnanyaKakani/}{\textcolor{blue}{\underline{LinkedIn}}} $|$
    \href{https://github.com/AnanyaKakani}{\textcolor{blue}{\underline{GitHub}}} $|$
    {\small Available: Spring Semester 2024}
\end {center}


%-----------Education-----------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Northeastern University}{Boston,MA}
      {MS in Informatics in Cloud Computing Concentration; \textbf{GPA: 3.86/4.0}} {Expected July 2024}

        {
    \vspace{1pt}
    Coursework - Enterprise Information Architecture, Cloud Analytics, Advanced Cloud Computing Management, Network Security and Cloud Security, Web Design and Development, AWS Cloud Architecting, Enterprise Data Storage and Management, ELECTIVE: UI/UX Design, Interactive Information Design 1}
% \textbf{GPA: 9.9/10}
      \resumeSubheading
      {Jawaharlal Nehru Technological University}{   Telangana, India}
      {Bachelor of Technology in Computer Science Engineering;  \textbf{GPA: 7.33/10.0}}{Aug 2017- Apr 2021}
      
      {
      \vspace{1pt}
      Coursework: Computer programming in C, Data Structures through C++, Object Oriented Programming through Java, DLD, DBMS, Computer Organization, Data Communication and Computer Networks, Web Technologies, Compiler Design, Python Programming, Data Mining, Cloud Computing, Cryptography and Network Security}
     
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{:Java, SQL, Python, JavaScript.} \\
    \textbf{Open Source Frameworks}{: Springboot, Spring Cloud, React, Django. } \\
     \textbf{Developer Tools}{:GitHub, VS Code, Eclipse, Jenkins} \\
     \textbf{Software Architecture}{: Microservice architecture (Spring Cloud, Eureka, Zookeeper, Zuul}\\
     \textbf{Other Technical skills}{: Postman, API Testing, Development, Collaboration}\\
    
     
     
     
     
    }}
 \end{itemize}
 


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northeastern University}{\textbf{Jan 2023 -- Present}}
     {Student Assistent} {Boston, MA}
      \resumeItemListStart
        \resumeItem{Maintaining access control using our access control system to confirm resident status, secure entry, and log in guests. Providing customer service to residents, guests, and visitors to the University.}
    \resumeItemListEnd
    \resumeSubheading
      {PricewaterhouseCoopers LLP}{\textbf{Sep 2021 -- Sep 2022}}
     {Associate Software Engineer } {Bangalore, India}
      \resumeItemListStart
        \resumeItem{I've gained practical expertise in Amazon Web Services (AWS) deployment where I have performed common platform tasks like AWS EC2, S3, RDS, Cloudwatch, etc.}
        \resumeItem{Developed new libraries with Micro Services architecture using Rest APIs, spring boot and pivotal cloud foundry and conducted end-to-end testing for microservices by achieving a remarkable 95\% efficiency rate.}
        \resumeItem{Transformed legacy application into a suite of cloud-hosted Microservices using Spring Boot, and laid the groundwork for x10 traffic scale.}
        \resumeItem{Worked in agile framework, collaborating with business and research teams in story grooming.}
        \resumeItem{I've also expanded my skills, including Spring Boot, Tableau, JWT authentication, and gateway transactions.}
       \resumeItem{I excel in designing both front-end and back-end solutions, following test-driven development principles to create robust and reliable software systems..}
        % \resumeItem{Sole responsible for Website development using Angular which reports and points the disparities for easy resolution.}
        \resumeItemListEnd
        \vspace{-2pt}
        \resumeItem{\textbf{Key Achievement}}
        \vspace{-5pt}
        \resumeItemListStart
        \resumeItem{Demonstrated effective communication and active engagement throughout the project. Awarded a Customer Appreciation Bonus for exceptional contributions. Honed leadership capabilities, becoming an integral part of the team.}
        \resumeItemListEnd
        
  %          

\section{Projects}
\vspace{-8pt}
    \resumeProjectHeading
        {\href{https://github.com/AnanyaKakani/skyline-project}{\textcolor{blue}{\textbf{Secure and Efficient Skyline Queries on Encrypted Data}}} \emph{$|$Python, Firebase, MySQL, Flask} }{\textbf{April 2021}}
        \resumeItemListStart
            \resumeItem{Developed a Flask-based web application to manage and visualize patient data.}
            \resumeItem{Integrated with Firebase Realtime Database for CRUD operations, ensuring real-time data access.}
            \resumeItem{Incorporated file upload features to store patient images and reports locally.}
            \resumeItem{Implemented Fernet encryption to ensure patient data confidentiality.}
            \resumeItem{Designed data visualization features using matplotlib to analyze and display disease trends and patient access data.}
            \resumeItem{Incorporated email functionality for notifications and communication, leveraging smtplib.}


     \resumeItemListEnd
     \vspace{1pt}
     \resumeProjectHeading
        {\href{https://github.com/AnanyaKakani/UpdatesOfCovid19}{\textcolor{blue}{\textbf{Updates of COVID-19}}} \emph{$|$ Java, DBMS, Serverlets, Hibernate ORM, SMTP Integration HTML/CSS, OOPS} }{\textbf{Dec 2020}}
        \resumeItemListStart
       
        \resumeItem{Transformed research paper insights into practical, adaptable algorithm, showcasing the application of academic knowledge.}
        \vspace{-10pt}
            \resumeItem{Articles: Users can view and post COVID-19 articles with images and video links.}
            \resumeItem{User Management: A registration and login system differentiates between regular and admin users.}
            \resumeItem{Hibernate: The application uses the Hibernate ORM for database interactions, with classes like Article and User mapping to database tables.}
            \resumeItem{Servlets: Java servlets manage functionalities such as user login and article processing.}
\resumeItemListEnd

     \vspace{1pt}
      \resumeProjectHeading
      {\href{}{
        {\textcolor{black}{\textbf{Pomodoro Web Timer}}} \emph{$|$Java, Spring Boot, Thymeleaf}}}{\textbf{Jan 2020}}
        \resumeItemListStart
        
            \resumeItem{Developed a web-based timer using the Pomodoro Technique.}
            \resumeItem{Used Spring Boot for the backend and Thymeleaf for dynamic HTML rendering.}
            \resumeItem{Added interactive controls with JavaScript for timer management}

\resumeItem{Styled the UI for a user-friendly experience on all devices.}
          \resumeItemListEnd
          \vspace{-12pt}
    \resumeProjectHeading
   
    % \resumeProjectHeading
    %     {\textbf{Detection of Propaganda from News Articles}}{\textbf{}}
    %     \resumeItemListStart
    %         \resumeItem{Employed CNN with GloVe pre-trained embedding and NLP techniques on the newspaper data to detect the presence of propaganda and achieved efficiency of 86.7\%.}
    %       \resumeItemListEnd


 \vspace{-8pt}


%-----------Hobbies-----------------
%\section{Hobbies/Interests}
%\begin{description}[font=\tiny$\bullet$]

%\small{
%\item {Exploring film and creative writing (storytelling) as outlets for imagination and work-life balance.}
%\end{description}


%-------------------------------------------

\end{document}\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Shiva Resume}
\author{Harin Kumar}
\date{April 2023}

\begin{document}

\maketitle

\section{Introduction}

\end{document}
